---
title: "A Simulation Study"
author: "Your name"
output: 
  html_document:
    theme: readable
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE
)
```

```{r packages 2, include=TRUE}
require(ggplot2)
require(reshape2)
```

```{r settings 2, include=TRUE}
theme_set(theme_bw())
```

Use the `tips` data from the `reshape2` package to reproduce the following graphics.  Hint: Among others, you may need to use the `ggplot2` functions:  `stat_summary()`, `theme()`, `facet_grid()`, `labs()`, `geom_jitter()`, `geom_boxplot()`, `geom_point()`, and `geom_smooth()`.    

# Comparaison de données {.tabset .tabset-pills}

## Mean comparaison two variables {-}
```{r}
# 1
ggplot(tips, aes(y = total_bill, x = sex, fill = sex)) +
  stat_summary(fun = "mean", geom = "bar", width = 0.05) +
  facet_grid(col = vars(smoker), labeller = label_both) +
  labs(y = "total_bill's mean") +
  theme(legend.position = "none") +
  labs(title = "Mean of total_bill by sex and smoker")
```

## visualization of data and mean {-}
```{r}
# 2
ggplot(tips, aes(x = sex, y = total_bill)) +
  geom_jitter(alpha = 0.2, width = 0.2, height = 0) +
  stat_summary(geom = "point", fun = "mean", size = 4, shape = 13, color = "red") +
  facet_grid(col = vars(smoker), labeller = label_both) +
  labs(title = "jitter of total_bill by sex and smoker. The mean for each group is indicated by a circle-cross")
```

## Boxplot comparison and bining {-}
```{r}
# 3
ggplot(tips, aes(x = cut(total_bill, breaks = c(3, 18, 25, 51)), y = tip)) +
  geom_boxplot(varwidth = TRUE) +
  facet_grid(col = vars(sex), labeller = label_both) +
  labs(x = "total_bill") +
  labs(title = "boxplot of tip by sex and total_bill (categorized)")
```
## adapt size to a variable {-}
```{r}
# 4
ggplot(tips, aes(x = total_bill, y = tip)) +
  geom_point() +
  aes(color = sex, size = size)
```

## data point comparison {-}
```{r}
# 5
ggplot(tips, aes(x = total_bill, y = tip)) +
  geom_point() +
  aes(color = sex) +
  facet_grid(row = vars(sex)) +
  theme(legend.position = "none")
```

## regression line depending on two variables {-}
```{r}
# 6
ggplot(tips, aes(x = total_bill, y = tip)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  aes(color = smoker) +
  facet_grid(row = vars(smoker), col = vars(sex), labeller = label_both) +
  theme(legend.position = "none")
```
