---  
title: "An RMarkdown report"
author: "Your name"
output:
  prettydoc::html_pretty:
    theme: architect
    df_print: paged
    toc: yes
  xaringan::moon_reader:
    nature:
      ratio: '16:9'
    self_contained: true 
    df_print: paged  
  pdf_document: default    
  rmdformats::readthedown: 
    df_print: paged
  word_document: default
  html_document: 
    theme: yeti
    highlight: kate
    df_print: paged
---   

```{r setup, include = FALSE}
require(knitr)

opts_chunk$set(
  echo = FALSE,
  comment = "",
  tidy = "styler",
  fig.align = "center",
  fig.width = 7,
  fig.asp = 0.62,
  out.width = "100%"
)

options(digits = 3)
```

```{r}
# Automatically set the variable xar to TRUE when 
# "output: xaringan::moon_reader" in the YAML
#The variable xar is used to get the xaringan presentation form this Rmd file   

xar <- names(rmarkdown::metadata$output[1]) == "xaringan::moon_reader"
```


## Data description

In this project we consider the classical `iris` data set that can be found in the base R package `datasets`. `iris` has 
_**`r ncol(iris)`**_
columns named 
_**`r paste(names(iris), collapse=", ")`**_ 
and 
_**`r nrow(iris)`**_  
observations. 

To get help about columns, run `?iris`. 

The data set `iris` is

```{r}
iris
```



<!-- see https://github.com/yihui/knitr/releases/tag/v1.37 -->
````{asis, echo = xar}
---
````


## Descriptive analysis

First, we compute some descriptive statistics with the `summary()` function:

```{r, R.options = list(knitr.kable.NA = "")}
summary(iris) |> kable(caption = "Descriptive statistics")
```

````{asis, echo = xar}
---
````

Second, we use the function `aggregate` to get the following table that shows the means of the $4$ numerical variables for each species.

```{r}
aggregate(cbind(Sepal.Length, Sepal.Width, Petal.Length, Petal.Width) ~ Species, data = iris, mean) |>
  kable(
    caption = "Means by species",
    col.names = c("Species", "Sepal Length", "Sepal Width", "Petal Length", "Petal Width")
  )
```

````{asis, echo = xar}
---
````

## Linear regression

We use the function `cor()` to get the Pearson's coefficients of correlation between all our numeric variables: 

```{r}
cor(iris[1:4]) |>
  kable(caption = "Pearson's coefficients of correlation")
```

````{asis, echo = xar}
---
````

Here are 3 scatter plots that show the association between `Petal.Length` and the other numerical variables. 

```{r}
#| fig.align = "default",
#| fig.show = "hold",
#| out.width = "50%",
#| fig.width = 5,
#| fig.asp = 0.8

par(mar = c(4, 4, 1, 1))

plot(Sepal.Length ~ Petal.Length, data = iris)
plot(Sepal.Width ~ Petal.Length, data = iris)
```

````{asis, echo = xar}
---
````

```{r}
#| fig.align = "default",
#| fig.show = "hold",
#| out.width = "50%",
#| fig.width = 5,
#| fig.asp = 0.8

par(mar = c(4, 4, 1, 1))

plot(Petal.Width ~ Petal.Length, data = iris)
```

````{asis, echo = xar}
---
````

Now, we would like to explain the variations in the length of the sepal as a function of the length of the petal. To do so, we use the following linear regression `lm(Sepal.Length ~ Petal.Length, data = iris)`. Here is the summary of this model:

```{r}
reg <- lm(Sepal.Length ~ Petal.Length, data = iris)
summary(reg)$coef |>
  kable(
    caption = "Summary of lm: Sepal.Length ~ Petal.Length",
    digits = c(3, 3, 3, 50)
  )
```


The model's equation is 
$$
\widehat{Sepal.Length} = `r coef(reg)[1]`+ `r coef(reg)[2]` Petal.Length.
$$


Here are the data with the regression line:

````{asis, echo = xar}
---
````

```{r}
#| fig.show = "hold",
#| out.width = "80%"

par(mar = c(4, 4, 1, 1))
plot(Sepal.Length ~ Petal.Length, data = iris, ylab = "Sepal length", xlab = "Petal length")
abline(reg)
```

````{asis, echo = xar}
---
````

Finally, we use the `plot(reg)` command to get some graphical representations of the residuals.

```{r}
#| fig.cap = "Residuals plot 1",
#| fig.align = "default",
#| fig.show = "hold",
#| out.width = "50%",
#| fig.width = 5,
#| fig.asp = 0.8

plot(reg, which = 1:2)
```

````{asis, echo = xar}
---
````

```{r}
#| fig.cap = "Residuals plot 2",
#| fig.align = "default",
#| fig.show = "hold",
#| out.width = "50%",
#| fig.width = 5,
#| fig.asp = 0.8

plot(reg, which = 3:4)
```
