---
title: "A Simulation Study"
author: "Your name"
output: 
  bookdown::html_document2:
    theme: readable
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
---

```{r, eval = F, echo = T}
title: "A Simulation Study"
author: "Your name"
output: 
  bookdown::html_document2:
    theme: readable
    highlight: tango
    toc: yes                   # c'est la table des matières
    toc_depth: 2               
    toc_float: yes             # Ici c'est le fait que ce soit sur le côté (plus stylé)
    number_sections: yes
```

```{r setup, include = TRUE, results='hide', message= FALSE}
require(knitr)

opts_chunk$set(
  echo = TRUE,
  comment = "",
  tidy = "styler",
  fig.align = "center",
  fig.width = 8,
  fig.asp = 0.62,
  out.width = "100%"
)

options(digits = 3)
```

```{r klippy, include=TRUE}
klippy::klippy(position = c("top", "right"))
```



```{r, eval = F, echo = T}
Le chunk ici permet de faire les panneaux joli c_est surtout le .tabset, 
le .tabset-pills permet de faire des ronds bleus

le {-} apres normal distribution c_est juste pour eviter d_ajouter le numero de section du YAML en haut. 

# Data {.tabset .tabset-pills}

## Normal distribution {-}

```



# Data {.tabset .tabset-pills}

## Normal distribution {-}

We first recall the definition of a normal random variable (displayed through a *quote* environment).


```{r, eval = F, echo = T}
# Ca c'est le truc bleu joli
> A random variable $X$ is said to be normally distributed with mean $\mu$ and
variance $\sigma^2$ if it has a probability density function $f:\mathbb{R}
\rightarrow \mathbb{R}^+$ given by
> $$
  f(x)=\frac{1}{\sqrt{2\pi}\sigma}\exp\left\{-\frac{(x-\mu)^2}{2 \sigma^2}\right\} (\#eq:nor)
  $$

```

> A random variable $X$ is said to be normally distributed with mean $\mu$ and
variance $\sigma^2$ if it has a probability density function $f:\mathbb{R}
\rightarrow \mathbb{R}^+$ given by
> $$
  f(x)=\frac{1}{\sqrt{2\pi}\sigma}\exp\left\{-\frac{(x-\mu)^2}{2 \sigma^2}\right\} (\#eq:nor)
  $$

This is written as $X \sim N(\mu, \sigma^2)$.

More details about normal random variables (r.v.) can be found on [this
page](https://en.wikipedia.org/wiki/Normal_distribution).

## Simulations {-}

The R function `rnorm` allows us to draw simulations from the normal density function as given by Equation \@ref(eq:nor). 

Let fix some parameters and generate some data.

```{r simul.param, echo=TRUE}
set.seed(1)
n <- 100
mu <- 100
stdev <- 2
v <- stdev^2
b0 <- 2
b1 <- 1
X <- rnorm(n, mu, stdev)
Y <- b0 + b1 * X + rnorm(n)
samp <- data.frame(X = X, Y = Y)
samp
```

As you can see, we draw _**`r n`**_ realizations from two random variables : $X \sim N$(_**`r mu`**_, _**`r v`**_) and $Y=b_0+b_1\times X+ \epsilon$, with $b_0=$ _**`r b0`**_, $b_1=$ _**`r b1`**_, and $\epsilon \sim N(0,1)$.

Observe that if you re- render the Rmd (source) file with different parameters `(n, mu, stdev, b0, b1)`, then all the numbers above get updated automatically. Check it!  

The simulated data will be use to fit a linear model, See the section [Linear model](#ll) .

# Descriptive statistics {.tabset .tabset-pills}

## Summary statistics {-}

* The empirical mean and variance of $X$ are  _**`r mean(samp$X) |> round()`**_ and _**`r var(samp$X) |> round()`**_, respectively.   

* The empirical mean and  variance of $Y$ are  _**`r mean(samp$Y) |> round()`**_ and _**`r var(samp$Y) |> round()`**_, respectively.

Let's summarize the simulations with the help of the `summary` function.

```{r, eval = F}
Lets summarize the simulations with the help of the `summary` function.
# le summary c'est avec altGr + 7
```

```{r}
summary(samp) |> kable()
```

## Histogram of X {-}

We can use the `hist` function to display, for example, the histogram of $X$:

```{r}
title.histX <- paste(" Hstogram of X, a Nomal R.V. with mean ", mu, " and varaince", v)
hist(samp$X, main = title.histX, xlab = "")
```

## Histogram of Y {-}

Similarly here is a histogram of $Y$:

```{r}
hist(samp$Y, main = "Hstogram of Y", xlab = "")
```


# Linear model {#ll .tabset .tabset-pills}

## The model {-}

We built a linear regression model using

```{r fit, echo=TRUE}
fit <- lm(Y ~ X, data = samp)
```

We get the following output

```{r}
summary(fit)$coef |>
  kable()
```

The coefficient of determination ($R^2)$ of this model is _**`r summary(fit)$r.squared `**_.

## Scatter plot with regression line {-}

```{r}
#| fig.cap="Fitted linear model"
plot(Y ~ X, data = samp)
abline(fit)
```

```{r, eval = F}
pour le caption de la figure il y a cette commande au dessus du plot 
#| fig.cap="Fitted linear model"
```

## Residuals and fitted values {-}

The model fitted values (`fitted`) and residuals (`fit$residuals`) are

```{r}
data.frame(fitted = fit$fitted.values, residuals = fit$residuals) |> round(3)
```

## Diagnostic plot {-}

```{r}
#| fig.cap="Residuals vs fitted values"
plot(fit$residuals ~ fit$fitted.values, xlab = "fitted", ylab = "residuals")
```
