---
title: "Exercice 1"
output: 
  bookdown::pdf_document2:
  df_print: kable
toc: false  
urlcolor: blue
linkcolor: blue   
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "",
  tidy = "styler",
  fig.align = "center",
  fig.width = 9,
  fig.asp = 0.62,
  out.width = "85%"
)

options(digits = 3)
```

```{r packages, include=FALSE}
require(kableExtra)
```

```{r data, echo=FALSE}
dataCar = read.csv("TP 1/Data/dataCar.csv")
```

**1.** The dimension of the data (num. of rows, num. of columns) is `r dm <- dim(dataCar)` (***`r dm[1]`***, ***`r dm[2]`***).

**2.** The first six lines of this data are

```{r, echo = T}
head(dataCar) |> kbl(booktabs = F) 
```
```{r, echo = T}
head(dataCar) |> kbl(booktabs = T) 
```
**3.** Using the R function `str()`, we get the structure of the data

```{r}
str(dataCar)
```

**4.** We made use of the function `subset()` to delete the first column of `dataCar` and the function `transform()` to transform the variables `clm`, `numclaims`, `veh_body`, `veh_age`, `gender`, `area`, and `agecat` to a factor. The summary of the resulting data is

```{r}
datCar <- subset(dataCar, select = -X)
datCar <- transform(dataCar,  clm = factor(clm),
                    numclaims = factor(numclaims),
                    veh_body = factor(veh_body),
                    veh_age = factor(veh_age),
                    gender = factor(gender),
                    area = factor(area),
                    agecat = factor(agecat))


summary(datCar)
```

**5.** Below is a Barplot of `numclaims`.

```{r}
#| fig.cap = 'Barplot of `numclaims`'

proportions(barplot(table(datCar$numclaims), xlab = "numclaims", ylab = "%"))
```


**6.** We define `dataCar0` to be the subset data with *only variables* `claimcst0` and `veh_value` and *only subjects* with (`claimcst0` $>0$) and (`agecat` $=3$ or $4$). In the flowing we will work with this data. Its summary appears below.

```{r}
datCar0 <- datCar |> subset(
  subset = (claimcst0 > 0) & (agecat == 3 | agecat == 4),
  select = c("claimcst0", "veh_value")
)

summary(datCar0)
```

**7.** We fit a linear regression model with `veh_value` as independent variable and `claimcst0` as dependent variable. We also fit another linear model but this time with `log(claimcst0)` as dependent variable. The summary of each model is given below.

-   claimcst0 \~ veh_value

```{r}
fit1 <- lm(claimcst0 ~ veh_value, data = datCar0)
summary(fit1)$coef
```

-   log(claimcst0) \~ veh_value

```{r}
fit2 <- lm(log(claimcst0) ~ veh_value, data = datCar0)
summary(fit2)$coef
```

**8.** We compute, for each model, a $95\%$ confidence intervals (confint) for the intercept and the slope parameters. We then use the `kableExtra` functions `kbl()`, `kable_styling()`, `pack_rows()` and `add_header_above()`, to construct the following table.

```{r, echo= T}
rbind(
  cbind(summary(fit1)$coef, confint(fit1)),
  cbind(summary(fit2)$coef, confint(fit2))
) |>
  kbl(
    booktabs = TRUE,
    linesep = "",
    digits = 3
  ) |>
  kable_styling(
    latex_options = "HOLD_position",
    position = "center"
  ) |>
  pack_rows("claimcst0~veh_value", 1, 2) |>
  pack_rows("log(claimcst0)~veh_value", 3, 4) |>
  add_header_above(c(" " = 4, "confint" = 3))
```

**9.** Figure \@ref(fig:fig1) below show the scatterplots "claimcst0\~veh_value" and "log(claimcst0)\~veh_value" (side by side) with the corresponding least squares regression lines.

```{r fig1, out.width="50%", fig.asp = 0.8, fig.align = "default", fig.show = "hold"}
#| fig.cap = 'Least Squares Regression Lines; (a) Y = claimcst0 and (b) Y = log(claimcst0)'

par(mar = c(5, 4, 2, 2))
plot(claimcst0 ~ veh_value, data = datCar0)
title(sub = "(a)")
abline(fit1, col = "blue")


plot(log(claimcst0) ~ veh_value, data = datCar0)
title(sub = "(b)")
abline(fit2, col = "blue")
```

To lean more about linear regression, visit the website of [Introduction to Modern Statistics](https://openintro-ims.netlify.app/model-slr.html#model-slr).
